\chapter{Theory}\todo{find a sutible name for this section}
\label{theory}
\section{Half-life}
In the research of finding radionuclides that can be used in medical applications like targeted radionucleide therapy, brachytherapy and PET-scans one have to look at the properties of the nuclides. One important property is the half-life, which can be divided into the physical half-life and the biological half-life. \todo{få med effective half life her}

\subsection{Physical half-life}
The physical half-life is the time it takes before half of the radionuclides have disintegrated. Radionucleides used in medical application can not have a short half-life as we need time to produce the radionucleides and separate it from other nuclei produced in the same reaction. In addition, if the radionuclides are not produced at the hospitals, we need some time transportation. The nuclei also require some time from it is injected into the patient until it has reached the cancer cells or the organs we would like to investigate. 
\vspace{3mm}
\\
On the other hand, a to long physical half-life is also not optimal as the patient will have radioactive nuclei in the body for a longer time, and expose surrounding people. To limit the dose for surrounding people, one would have to isolate the patient for a longer time period. This would make the treatment more expensive and will be a bigger burden for the patient. An ideal range for the physical half-life for radionucleides used in medical applications is between $6$ h and $7$ d \cite{yeongTherapeuticRadionuclidesNuclear2014a}.

\subsection{Biological half-life}
The biological half-life is defined as the time it takes for the body to get rid of half of the radionuclides and depends on the tracer used. If the biological half-life is long the physical half-life should not be too long as discussed above. A short biological half-life on the other hand, could open for the use of longer lived radionucleides as the nuclei will be emitted form the body and prevent the need for a long isolation period. However, if the biological half-life is too short, the nuclei will be submitted with a high activity. Hence, extra conciderations regarding the waste management would be needed \cite{yeongTherapeuticRadionuclidesNuclear2014a}.



\section{Stopping power and linear energy transfer (LET)}
Biologisk effekt og at vi ønsker høy LET, men kort range osv

\section{Brachytherapy}
\section{PET-scans}
\section{My ytrium isotopes}


